E-Graphs With Bindings

### 2025-01-19 LICS_2025/e_graphs_with_bindings/sections/appendix.tex
wip

  This makes $\catname{SLat}$ a suitable base for enrichment and allows us to take $\mathcal{V} = \catname{SLat}$.

@@

    \begin{proposition}[Special case of Proposition 6.4.6~\cite{Borceux_1994}]
      The forgetful functor $U : \catname{SLat} \to \catname{Set}$ has a left adjoint free functor $F : \catname{Set} \to \catname{SLat}$.
    \end{proposition}
    \begin{proof}
      The functor $F$ is defined by letting $F(A) = \coprod_{A} I_{\catname{SLat}}$ where the latter is a coproduct which is a `free' product of semilattices defined as follows.
      The elements of $S_{1} \coprod S_{2}$ are sequences $s_{1} + s_{2} + \ldots + s_{n}$ where each $s_{i}$ is either from $S_{1}$ or $S_{2}$ quotiented by all relations in $S_{1}$ and $S_{2}$.
      The adjunction is then given by the following natural isomorphisms
      \[
      \catname{SLat}(\coprod_{A}(I_{\catname{SLat}}), B) \cong \prod_{A}(\catname{SLat}(I_{\catname{SLat}}, B)) \cong \catname{Set}(A,\catname{SLat}(I_{\catname{SLat}}, B)) \cong \catname{Set}(A, U(B))
      \]
      The fist isomorphism is given by the fact that hom-functor makes limits into colimits in its first argument, the second being given by the property that $|\catname{Set}(A,B)| = |B|^{|A|} = |\underbrace{B \times \ldots \times B}_{|A|}|$, and the last isomorphism is given by the definition of $U$.
      Furthermore, we have, 
      \[
      F(I) \cong I_{\catname{SLat}}
      \]
      and 
      \begin{align*}
      F(A) \otimes F(B) &\cong (\coprod_{A} I_{\catname{SLat}}) \otimes (\coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A} (I_{\catname{SLat}} \otimes \coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A} (\coprod_{B} (I_{\catname{SLat}} \otimes I_{\catname{SLat}}))\\
            &\cong \coprod_{A} (\coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A \times B} I_{\catname{SLat}}\\
            &\cong F(A \times B)
      \end{align*}
    In the above we used the fact that functors $- \otimes X$ and $X \otimes -$ preserve colimits as they are both left-adjoint by symmetry and monoidal closedness of $\catname{SLat}$.
    \end{proof}

\section{Proofs for Section \ref{sec:e-hypergraphs}: E-hypergraphs}
\label{sec:appendix:2}

In this section we will define the conditions under which the pushout in $\catname{EHyp}(\Sigma)$ exists and we will explicitly construct such a pushout.
We will also show the uniqueness of a boundary pushout complement.
These condition will play a crucial role in showing that for each enrichment equation in $\textbf{PROP}^{+}(\Sigma)$ there is a sequence of rewrites in $\WellTypedMdaEcospans$.

\begin{proposition}
    Two cospans in $\catname{Hyp}(\Sigma)$ (\textit{i.e.}, morphisms in $\HypI{\Sigma}$) $n \xrightarrow{f} \mathcal{G} \xleftarrow{g} m$ and $n \xrightarrow{f'} \mathcal{G}' \xleftarrow{g'} m$ are equal if and only if
    the following two cospans  $\catname{EHyp}(\Sigma)$ (\textit{i.e.} morphisms in $\Ecospans$)
    \[
    n \xrightarrow{f_{ext}} n \xrightarrow{f_{int}} \mathcal{G} \xleftarrow{g_{int}} m \xleftarrow{g_{ext}} m
    \]
    \[
        n \xrightarrow{f_{ext}'} n \xrightarrow{f_{int}'} \mathcal{G} \xleftarrow{g_{int}'} m \xleftarrow{g_{ext}'} m    
    \]
    such that $f = f_{ext};f_{int}, f'=f_{ext}';f_{int}'$ (respectively, $g = g_{ext};g_{int}, g' = g_{ext}';g_{int}'$) are equal.
\end{proposition}
This essentially means that $\catname{\HypI{\Sigma}}$ faithfully embeds into $\Ecospans$. 
\begin{proof}
    Recall that cospans are equal when they are isomorphic.
    The proposition means that the following cospans are isomorphic (where $\alpha$ is an isomorphism)
    \[\begin{tikzcd}
            & \mathcal{G} \arrow[dd, "\alpha"] &                                                            \\
    n \arrow[ru, "f", bend left] \arrow[rd, "f'"', bend right] &                                  & m \arrow[lu, "g"', bend right] \arrow[ld, "g'", bend left] \\
            & \mathcal{G}'                     &                                                           
    \end{tikzcd}
    \]
    if and only if the following cospans are isomorphic
    \[
        \begin{tikzcd}
            & n \arrow[r, "f_{int}"] \arrow[dd, "\beta"] & \mathcal{G} \arrow[dd, "\alpha"] & m \arrow[l, "g_{int}"'] \arrow[dd, "\gamma"] &                                                                        \\
n \arrow[ru, "f_{ext}", bend left] \arrow[rd, "f_{ext}'"', bend right] &                                            &                                  &                                              & m \arrow[lu, "g_{ext}"', bend right] \arrow[ld, "g_{ext}'", bend left] \\
            & n \arrow[r, "f_{int}'"']                    & \mathcal{G}'                     & m \arrow[l, "g_{int}'"]                      &                                                                       
\end{tikzcd}    
    \]
    such that $f = f_{ext};f_{int}, f'=f_{ext}';f_{int}'$ (respectively, $g = g_{ext};g_{int}, g' = g_{ext}';g_{int}'$).
    The direction from right to left is straightforward: since the bottom diagram commutes $f;\alpha = f_{int};f_{ext};\alpha = f_{int}';f_{ext}' = f'$ and similarly for $g$.

    Let's show the direction from left to right.
    Note that $f_{ext}$ and $f_{ext}'$ have inverses since they are injective and surjective (the injection is per the definition and surjection is because domain and codomain are equal).
    Then we need $f_{ext};\beta = f_{ext}'$ and we define $\beta = f_{ext}^{-1};f_{ext}'$.
    Similarly $\beta^{-1} = f_{ext}'^{-1};f_{ext}$. 
    We can check that $\beta^{-1};\beta = f_{ext}'^{-1};f_{ext};f_{ext}^{-1};f_{ext}' = f_{ext}'^{-1};id;f_{ext}' = f_{ext}'^{-1};f_{ext}' = id$.
    Then we have that $f_{ext};\beta;f_{int}' = f_{ext};f_{ext}^{-1};f_{ext}';f_{int}' = f_{ext}';f_{int}' = f' = f;\alpha = f_{ext};f_{int};\alpha$.
    Since $f_{ext}$ is surjective, we have $\beta;f_{int}' = f_{int};\alpha$.
    Analogously for $\beta^{-1}$ and the right-hand sides of the diagrams.
\end{proof}

\subsection{Existence of pushout}

In constructing the pushout the functional versions of e-hypergraph relations will be useful.
\begin{remark}
    Both $<$ and $\consistency$ can be considered as (partial) functions defined on $V_{\mathcal{F}} + E_{\mathcal{F}}$, \textit{i.e.}, on the coproduct of vertices and edges.
    To make things well-typed, we will use corresponding coproduct injections $\iota_{V} : {V_{\mathcal{F}}} \to V_{\mathcal{F}} + E_{\mathcal{F}}$ and $\iota_{E} : {E_{\mathcal{F}}} \to V_{\mathcal{F}} + E_{\mathcal{F}}$ when passing either a vertex or an edge into these functions.
    For example, an immediate successor of a vertex $x$ can be written functionally as $<_{\mathcal{F}}^{\mu}(\iota_{V_{\mathcal{F}}}(x))$.
\end{remark}

\begin{remark}
    Using functional notation we can reformulate the notion of a homomorphism between two e-hypergraphs in the following way.
\end{remark}
\begin{definition}
        \label{def:e-homo-2}    
        A \emph{homomorphism} $\phi: \mathcal{F} \to \mathcal{G}$ of e-hypergraphs $\mathcal{F},\mathcal{G}$ is a pair of functions $\phi_V : V_{\mathcal{F}} \to V_{\mathcal{G}}, \phi_E : E_{\mathcal{F}} \to E_{\mathcal{G}}$ such that

        \begin{enumerate}
            \item $\phi$ is hypergraph homomorphism.

            \item When $x$ is not a top-level vertex, 
                \[
                \phi_{E}(<_{\mathcal{F}}^{\mu}(\iota_{V_{\mathcal{F}}}(x))) = <_{\mathcal{G}}^{\mu}(\phi_{V};\iota_{V_{\mathcal{G}}}(x))
                \]
                and
                \[
                \phi_{E}(<_{\mathcal{F}}^{\mu}(\iota_{E_{\mathcal{F}}}(x))) = <_{\mathcal{G}}^{\mu}(\phi_{E};\iota_{E_{\mathcal{G}}}(x))  
                \] when $x$ is a not top-level edge.
                \item
            When $x \in E_{\mathcal{F}}$
            \[
                [\phi_{V};\iota_{V_{\mathcal{G}}}, \phi_{E};\iota_{E_{\mathcal{G}}} ]^{*}(\consistency_{\mathcal{F}}(\iota_{E_{\mathcal{F}}}(x)))
                \subseteq
                \consistency_{\mathcal{G}}(\phi_{E};\iota_{E_{\mathcal{G}}}(x))
            \]
            where $\phi_{V};\iota_{V_{\mathcal{G}}} : V_{\mathcal{F}} \to V_{\mathcal{G}} + E_{\mathcal{G}}$, and similarly for $\phi_{E};\iota_{E_\mathcal{G}}$ so that $[\phi_{V};\iota_{V_{\mathcal{G}}}, \phi_{E};\iota_{E_{\mathcal{G}}}] : V_{\mathcal{F}} + E_{\mathcal{F}} \to  V_{\mathcal{G}} + E_{\mathcal{G}}$.
            \item When $x \in V_{\mathcal{F}}$
            \[
                [\phi_{V};\iota_{V_{\mathcal{G}}}, \phi_{E};\iota_{E_{\mathcal{G}}}]^{*}(\consistency_{\mathcal{F}}(\iota_{V_{\mathcal{F}}}(x)))
                \subseteq
                \consistency_{\mathcal{G}}(\phi_{V};\iota_{V_{\mathcal{G}}}(x)).
            \]
            \end{enumerate}
\end{definition}

\begin{theorem}[Existence of pushouts in $\catname{EHyp}(\Sigma)$]
\label{th:existence_of_pushouts}
Consider the following span in $\catname{EHyp}(\Sigma)$
% https://q.uiver.app/#q=WzAsMyxbMCwwLCJaIl0sWzIsMCwiWCJdLFswLDIsIlkiXSxbMCwxLCJmIl0sWzAsMiwiZyIsMl1d
\[\begin{tikzcd}
	Z && X \\
	\\
	Y
	\arrow["f", from=1-1, to=1-3]
	\arrow["g"', from=1-1, to=3-1]
\end{tikzcd}\]
such that
\begin{enumerate}
\label{pushout:assumptions}
    \item $Z$ is a \textit{discrete} e-hypergraph.
    \item \label{assumption:equal_predecessors} $[f_{V}(v_i)) = [f_{V}(v_j))$ and $[g_{V}(v_i)) = [g_{V}(v_j))$ for all $v_{i},v_{j}$ in $V_{Z}$.
    \item \label{assumption:non_ambiguous_predecessors} If $[f_{V}(v)) \not = \varnothing$ then $[g_{V}(v)) = \varnothing$ and if $[g_{V}(v)) \not = \varnothing$ then $[f_{V}(v)) = \varnothing$.
    \item $\consistency(f_{V}(v_i)) = \consistency(f_{V}(v_j))$ and $\consistency(g_{V}(v_i)) = \consistency(g_{V}(v_j))$ for all $v_i,v_j$ in $V_{Z}$.
\end{enumerate}    
then the pushout $X +_{f,g} Y$ exists.
\end{theorem}
\begin{proof}
    Consider the diagram below.
    \[
        \adjustbox{scale=1.25}{
            \begin{tikzcd}
            Z \arrow[r, "f"] \arrow[d, "g"']                                   & X \arrow[d, "\sfrac{\iota_1}{\sim R}"] \arrow[rdd, "j_1", bend left] &   \\
            Y \arrow[r, "\sfrac{\iota_2}{\sim R}"] \arrow[rrd, "j_2"', bend right] & \sfrac{X+Y}{\sim R} \arrow[rd, "u"]                              &   \\
                                                                            &                                                                  & Q
            \end{tikzcd}}
    \]
    Then, the pushout of e-hypergraphs $X$ and $Y$ is computed in two steps.
    First, a coproduct of $X+Y$ is computed which is 
    \[
        X + Y = \{V_{X} + V_{Y}, E_{X} + E_{Y}, s_{X+Y}, t_{X+Y}, \consistency_{X+Y}, <_{X+Y} \}
    \]
    where $s_{X+Y} : E_{X} + E_{Y} \to (V_{X} + V_{Y})^{*}$ which can be defined as a copairing $[s'_{X}, s'_{Y}] : E_{X} + E_{Y} \to (V_{X} + V_{Y})^{*}$ and $s'_{X} : E_{X} \to (V_{X} + V_{Y})^{*}$, $s'_{Y} : E_{Y} \to (V_{X} + V_{Y})^{*}$ defined as $s'_{X} = s_{X};\iota_{1,V}^{*}$ and $s'_{Y} = s_{Y};\iota_{2,V}^{*}$ where $\iota_1,\iota_2$ are corresponding coproduct injections, similarly for $t_{X+Y}, <_{X+Y}, \consistency_{X+Y}$.
    We will omit labels as they are irrelevant to pushout construction.
    Consider relations
    \ifdefined\ONECOLUMN
    \begin{align*}
            S_{V} &= \;\{
            (x_i,y_j) \in (V_{X} + V_{Y}) \times (V_{X} + V_{Y})\; |
            \exists z \in V_{Z} \; . \; x_i = f_{V};\iota_{1,V}(z) \text{ and }\\
            &\qquad y_j = g_{V};\iota_{2,V}(z) \text{ where $x_i \in V_{X}$ and $y_j \in V_{Y}$ }
            \}\\
            &\cup \;\{
                (y_j,x_j) \in (V_{X} + V_{Y}) \times (V_{X} + V_{Y})\; |
          \exists z \in V_{Z} \; . \; x_i = f_{V};\iota_{1,V}(z) \text{ and }\\
          &\qquad y_j = g_{V};\iota_{2,V}(z) \text{ where $x_i \in V_{X}$ and $y_j \in V_{Y}$ }
        \}\\
        &\cup \;\{(x,x)\;\text{where}\; x \in V_{X} + V_{Y}\}\\
        S_{E} &= \;\{(x,x) \text{ where } x \in E_{X} + E_{Y}\}
    \end{align*}
    \else 
    \begin{align*}    
    S_{V} &= \{\\
          &\;(x_i,y_j) \in (V_{X} + V_{Y}) \times (V_{X} + V_{Y})\; | \\
          &\;\exists z \in V_{Z} \; . \; x_i = f_{V};\iota_{1,V}(z) \text{ and } y_j = g_{V};\iota_{2,V}(z)\\
          &\;\text{ where $x_i \in V_{X}$ and $y_j \in V_{Y}$ }\\
          &\}\\
          &\cup\\
          &\{\\
          &\;(y_j,x_j) \in (V_{X} + V_{Y}) \times (V_{X} + V_{Y})\; | \\
          &\;\exists z \in V_{Z} \; . \; x_i = f_{V};\iota_{1,V}(z) \text{ and } y_j = g_{V};\iota_{2,V}(z)\\
          &\;\text{ where $x_i \in V_{X}$ and $y_j \in V_{Y}$ }\\
          &\}\\
          &\cup\\
          &\{\\
          &\;(x,x)\;\text{where}\; x \in V_{X} + V_{Y}\\
          &\}\\
        \\
    S_{E} &= \{(x,x) \text{ where } x \in E_{X} + E_{Y}\}
    \end{align*}
    \fi
    % \begin{align*}
    % S_{E} &= \{\\
    % &(x_i,y_j) \in (E_{X} + E_{Y}) \times (E_{X} + E_{Y})\; |\\
    % &\exists z \in E_{Z} \; . \; x_i = f_{E};\iota_{1,E}(z) \text{ and } y_j = g_{E};\iota_{2,E}(z)\\
    % &\text{ where $x_i \in E_{X}$ and $y_j \in E_{Y}$}\\
    % &\}
    % \end{align*}
and let relations $R_{V},R_{E}$ be their transitive closures respectively.

We then quotient the set vertices and edges in $X + Y$ by $R_{V}$ and $R_{E}$ respectively.
\ifdefined \ONECOLUMN
\begin{align*}
    \sfrac{X + Y}{\sim (R_{V},R_{E})} = \{
        &\sfrac{V_{X} + V_{Y}}{\sim (R_{V},R_{E})}, \sfrac{E_{X} + E_{Y}}{\sim (R_{V},R_{E})}, \sfrac{s_{X+Y}}{\sim (R_{V},R_{E})},\\
        &\sfrac{t_{X,Y}}{\sim (R_{V},R_{E})}, \consistency_{\sfrac{X+Y}{\sim (R_{V},R_{E})}}, <_{\sfrac{X + Y}{\sim (R_{V},R_{E})}}\}    
\end{align*}
\else
    \begin{align*}
        \sfrac{X + Y}{\sim (R_{V},R_{E})} = \{&\\
            &\sfrac{V_{X} + V_{Y}}{\sim (R_{V},R_{E})}, \sfrac{E_{X} + E_{Y}}{\sim (R_{V},R_{E})}, \sfrac{s_{X+Y}}{\sim (R_{V},R_{E})},\\
            &\sfrac{t_{X,Y}}{\sim (R_{V},R_{E})}, \consistency_{\sfrac{X+Y}{\sim (R_{V},R_{E})}}, <_{\sfrac{X + Y}{\sim (R_{V},R_{E})}}\\
        & \}    
    \end{align*}
\fi
We will refer to $\sim (R_{V},R_{E})$ just as $\sim$, \textit{e.g.}, by writing $\sfrac{V_{X} + V_{Y}}{\sim}$ and concrete relation will be clear from the context.
Where necessary we will refer to $S_{V}$ and $S_{R}$ as $\sim_{S}$.
We have 
\[
    \sfrac{s_{X+Y}}{\sim} : \sfrac{E_{X} + E_{Y}}{\sim} \to (\sfrac{V_{X} + V_{Y}}{\sim})^{*}
\]
and there is an obvious surjective function $[]_{V} : (V_{X} + V_{Y}) \to (\sfrac{V_{X} + V_{Y}}{\sim})$ that maps elements to their equivalence classes and $[]_{V}^{*}$ is its extension to sequences.
There is also $[] : E_{X} + E_{Y} \to \sfrac{E_{X} + E_{Y}}{\sim}$ and we will omit subscripts as the correct type will be clear from the argument.
We then define 
\[
    \sfrac{s_{X+Y}}{\sim}([e]) = s_{X+Y};[]^{*}(e) = [s_{X+Y}(e)]^{*}
\]
We will also use subscripts when it is important to tell if an element of $E_{X} + E_{Y}$ has a pre-image in either $E_{X}$ or $E_{Y}$ by writing $e_{x}$ or $e_{y}$.
Similarly, we will write $v_{x}$ to refer to a vertex with a pre-image in $V_{X}$.
Likewise, 
\[
    t_{\sfrac{X+Y}{\sim}}([e]) = [t_{X+Y}(e)]^{*}
\]

These definitions make $([]_{V},[]_{E})$ automatically a homomorphism with respect to source and target maps.
These maps are also automatically well-defined functions since $[e_1] = [e_2]$ implies $e_1 = e_2$ since the mappings for edges are mono.

% So far, the construction matches the construction of the pushout in $\catname{Hyp_{\Sigma}}$ which can be found in~\cite{bonchi_string_2022-1} and hence $s_{\sfrac{X+Y}{\sim}}$ and $t_{\sfrac{X+Y}{\sim}}$ are well-defined and $[]$ is a homomorphism with respect to sources and targets and therefore $\sfrac{\iota_1}{\sim}$ and $\sfrac{\iota_{2}}{\sim}$ are.

Recall that $<$ is essentially a transitive closure of $<^{\mu}$ and hence we can first define 
    \[<_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{E_{X} + E_{Y}}{\sim}}[e])
    \] and 
    \[
        <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}[u])
    \] where $\iota_*$ are injections into $\sfrac{V_{X} + V_{Y}}{\sim} + \sfrac{E_{X} + E_{Y}}{\sim}$.
    We will consider several cases.
    First, assume that $u$ is an element of $V_{X+Y}$ and
    \begin{enumerate}
        \item If there exists $v$ such that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v))$ is defined and $u \sim v$
              we let
              \[
                <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}([u])) = [<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v))]
              \]
        \item \label{def:child_respects_connectivity} $u$ has no pre-image in $V_{Z}$ and $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(u))$ is undefined (\textit{i.e.}, $[u) = \varnothing$).
              If there exists $v$ such that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v)) = e'$ and such that there is an \textit{undirected} path from $[u]$ to $[v]$, then we define
              \[ 
                <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}[u]) = <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}[v])
              \]
    \end{enumerate}
    Note that the existence of a path in the definition (2) implies that there exists $v' \sim v$ such that there is a path from $u$ to $v'$ and furthermore $v \not = v'$.
    If $v' = v$ then it would mean that $[u) \not = \varnothing$ since $[v) \not = \varnothing$ and there is a path from $u$ to $v$.
    There is no case when $u$ has a pre-image in $V_{Z}$ and yet $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(u))$ is undefined and there exists $v$ such that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v)) = e$ and there is a path from $[u]$ to $[v]$.
    The existence of a path would mean that there is $u' \sim u$ and $v' \sim v$ such that there is a path from $u'$ to $v'$ and since $u$ has a pre-image in $V_{Z}$, $u = f_{V};\iota_{1,V}(z_1)$.
    $v' \sim v$ means that both $v'$ and $v$ have a pre-image in $V_{Z}$ (unless $v' = v$ in which case $[u') \not = \varnothing$ as there is a path from $u'$ to $v'$) and since $u = f_{V};\iota_{1,V}(z_1)$ and $[u) = \varnothing$ $f_{V};\iota_{1,V}(z) = \varnothing$ for all $z$.
    Since $[v) \not = \varnothing$ and $v' \sim v$, $v$ is necessarily in the image of $g_{V};\iota_{2,V}$ and for all $z$ $[g_{V};\iota_{2,V}(z)) \not = \varnothing$ as well as for some $z'$ such that $u'' = g_{V};\iota_{2,V}(z')$ and $u'' \sim_{S} u$ which would mean that the case (1) is applicable to $u$.
    Similarly, when $u = g_{V};\iota_{2,V}(z)$.

    Otherwise, we leave $<_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}([u]))$ undefined.
    % \question{In the case when images of $f$ and $g$ are top-level the function is undefined. Shall we introduce bottom?}
    Now, assume that $e$ is an element of $E_{X+Y}$.
    Consider two cases.
    \begin{enumerate}
    \item  $<_{X+Y}^{\mu}(\iota_{E_{X} + E_{Y}}(e)) = e'$.
            Then we define
        \[
            <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{E_{X} + E_{Y}}{\sim}}[e]) = [<_{X+Y}^{\mu}(\iota_{E_{X} + E_{Y}}(e))]
        \]
    \item $[e) = \varnothing$ and there exists $v$ such that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v)) = e'$ and such that there is an undirected path from $[e]$ to $[v]$, we define 
        \[
            <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{E_{X} + E_{Y}}{\sim}}[e]) = <_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{\sfrac{V_{X} + V_{Y}}{\sim}}[v])
        \] 
    \end{enumerate}
    Otherwise we leave $<_{\sfrac{X+Y}{\sim}}^{\mu}(\iota_{E_{X} + E_{Y}}{\sim}([e]))$ undefined.
    % We will also build this relation in steps, first we do steps for vertices (1) - (3), then step (1) for edges and finally, we will interleave step (2) for edges and step (4) for vertices until fixed point.
    % Essentially, this interleaving means that vertices inherit the relation from incident edges and vice versa.
    Clearly, all the cases above are disjoint.

    Let's show that the definition does not depend on a particular choice of $v$ in (1).
    Suppose there exist $v_1$ and $v_2$ such that $v_1 \not = v_2$ and $[v_1) \not = \varnothing$ and $[v_2) \not = \varnothing$ and such that $u \sim v_1$ and $u \sim v_2$.
    Then, it must be the case that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_1)) = <_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_2))$.
    Consider cases.
    \begin{itemize}
        \item $u = v_1$ and $u \sim_{S} v_2$. Then there exists $z \in V_{Z}$ such that $u = f_{V};\iota_{1,V}(z) = v_1$ and $v_2 = g_{V};\iota_{2,V}(z)$.
              Since $[v_1) \not = \varnothing$, it must be the case that $[v_2) = \varnothing$ according to assumption \ref{assumption:non_ambiguous_predecessors} and we get a contraction to $[v_2) \not = \varnothing$.
        \item $u = v_1$ and $u \sim v_2$. The latter implies that $u$ has a pre-image in $V_{Z}$ and so does $v_2$.
              For both $[v_1) \not = \varnothing$ and $[v_2) \not = \varnothing$ they should be both in the image of $f_{V};\iota_{1,V}$ or $g_{V};\iota_{2,V}$ and according to assumption \ref{assumption:equal_predecessors} their sets of predecessors must be equal.
        \item $u \sim_{S} v_1$ and $u \sim_{S} v_2$. This implies $u = f_{V};\iota_{1,V}(z_1) = f_{V};\iota_{1,V}(z_2)$ and $v_{1} = g_{V};\iota_{2,V}(z_1)$ and $v_{2} = g_{V};\iota_{2,V}(z_2)$.
              By assumption \ref{assumption:equal_predecessors} it must be the case that $[g_{V}(z_1)) = [g_{V}(z_2))$ which implies that $[v_1) = [v_2)$.
              The case when $u = g_{V};\iota_{2,V}(z_1)$ is symmetric.
        \item $u \sim v_1$ and $u \sim v_2$. Same as above, by assumption \ref{assumption:non_ambiguous_predecessors} both $v_1$ and $v_2$ should be in the image of $f_{V};\iota_{1,V}$ or $g_{V};\iota_{2,V}$ and by assumption \ref{assumption:equal_predecessors} $[v_1) = [v_2)$.
    \end{itemize}

    Let's show that the definition does not depend on a particular choice of $v$ in (2).
    Suppose, $[u) = \varnothing$ and there exist $v_1$ and $v_2$ such that $<_{X+Y}^{\mu}(v_1) = e_1$ and $<_{X+Y}^{\mu}(v_2) = e_2$ and $e_1 \not = e_2$ and such that there is a path from $[u]$ to $[v_1]$ and from $[u]$ to $[v_2]$.
    The existence of a path from $[u]$ to $[v_1]$ means that there is $v_1' \sim v_1$ such that there is a path from $u'$ to $v_1'$ and similarly for $v_2$ and $v_2'$.
    We will proceed by case analysis.
    \begin{itemize}
            \item If $v_1 = v_1'$ or $v_2 = v_2'$ it means that there is a path from $u$ to $v_1$ or from $u$ to $v_2$ and since $[v_1) \not = \varnothing$ as well as $[v_2) \not = \varnothing$ it must be the case that $[u) \not = \varnothing$ which contradicts the assumption that $[u) = \varnothing$.
            \item Suppose $v_1 \sim_{S} v_1'$ which means there exists $z_1 \in V_{Z}$ such that $v_1 = f_{V};\iota_{1,V}(z_1)$ and $v_1' = g_{V};\iota_{2,V}(z_1)$ and suppose $v_2 \sim_{S} v_2'$ which further means there exists $z_2 \in V_{Z}$ such that $v_2 = f_{V};\iota_{1,V}(z_2)$ and $v_2' = g_{V};\iota_{2,V}(z_2)$.
                  Then we have
                  \begin{align*}
                    <_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_1)) &= <_{X+Y}^{\mu}(f_{V};\iota_{1,V};\iota_{V_{X} + V_{Y}}(z_1))\\
                                                              &= \iota_{1,E}(<_{X}^{\mu}(f_{V};\iota_{V_{X}}(z_1)))
                \end{align*}
                  and
                  \begin{align*}
                    <_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_2)) &= <_{X+Y}^{\mu}(f_{V};\iota_{1,V};\iota_{V_{X} + V_{Y}}(z_2))\\
                                                              &= \iota_{1,E}(<_{X}^{\mu}(f_{V};\iota_{V_{X}}(z_2)))
                \end{align*}
                and $e_1 \not = e_2$ implies $<_{X}^{\mu}(f_{V};\iota_{V_{X}}(z_1)) \not = <_{X}^{\mu}(f_{V};\iota_{V_{X}}(z_2))$ which contradicts the assumption \ref{assumption:equal_predecessors}.
                The case if $v_2 = g_{V};\iota_{2,V}(z_2)$ and $v_1 = f_{V};\iota_{1,V}(z_1)$ ultimately contradicts the assumption \ref{assumption:non_ambiguous_predecessors} as it entails that both
                \[
                    <_{X}^{\mu}(f_{V};\iota_{V_{X}}(z_1)) \not = \varnothing
                \]
                and
                \[
                    <_{Y}^{\mu}(g_{V};\iota_{V_{Y}}(z_2)) \not = \varnothing
                \]
                The cases when $v_1 = g_{V};\iota_{2,V}(z_1)$ and $v_2 = f_{V};\iota_{1,V}(z_2)$, and $v_1 = g_{V};\iota_{2,V}(z_1)$ and $v_2 = g_{V};\iota_{2,V}(z_2)$ are analogous.
            \item Suppose $v_1 \sim_{S} v_1'$ and $v_2 \sim v_2'$ via $w = (x_1, \ldots, x_n)$ such that there is a path from $u$ to $v_1'$ and from $u$ to $x_n = v_2'$.
                  The mere fact that $v_2 \sim v_2'$ implies that $v_2$ should have a pre-image in $V_{Z}$ and the same holds for $v_1$.
                  By the same reasoning as above it must be the case that $<_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_1)) = <_{X+Y}^{\mu}(\iota_{V_{X} + V_{Y}}(v_2))$.
            \item The case $v_1 \sim v_1'$ via $w = (x_1, \ldots, x_n)$ and $v_2 \sim_{S} v_1$ is symmetric to the above.
            \item The case when $v_1 \sim v_1'$ and $v_2 \sim v_2'$ is analogous.
    \end{itemize}

>>>>

  This makes $\catname{SLat}$ a suitable base for enrichment.

@@

    \begin{proposition}[Special case of Proposition 6.4.6~\cite{Borceux_1994}]
      The forgetful functor $U : \catname{SLat} \to \catname{Set}$ has a left adjoint free functor $F : \catname{Set} \to \catname{SLat}$.
    \end{proposition}
    \begin{proof}
      The functor $F$ is defined by letting $F(A) = \coprod_{A} I_{\catname{SLat}}$ where the latter is a coproduct which is a `free' product of semilattices defined as follows.
      The elements of $S_{1} \coprod S_{2}$ are sequences $s_{1} + s_{2} + \ldots + s_{n}$ where each $s_{i}$ is either from $S_{1}$ or $S_{2}$ quotiented by all relations in $S_{1}$ and $S_{2}$.
      The adjunction is then given by the following natural isomorphisms
      \begin{align*}
      \catname{SLat}(\coprod_{A}(I_{\catname{SLat}}), B) &\cong \prod_{A}(\catname{SLat}(I_{\catname{SLat}}, B))\\
                                                         &\cong \catname{Set}(A,\catname{SLat}(I_{\catname{SLat}}, B))\\
                                                         &\cong \catname{Set}(A, U(B))
      \end{align*}
      The fist isomorphism is given by the fact that hom-functor makes limits into colimits in its first argument, the second being given by the property that $|\catname{Set}(A,B)| = |B|^{|A|} = |\underbrace{B \times \ldots \times B}_{|A|}|$, and the last isomorphism is given by the definition of $U$.
      Furthermore, we have, 
      \[
      F(I) \cong I_{\catname{SLat}}
      \]
      and 
      \begin{align*}
      F(A) \otimes F(B) &\cong (\coprod_{A} I_{\catname{SLat}}) \otimes (\coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A} (I_{\catname{SLat}} \otimes \coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A} (\coprod_{B} (I_{\catname{SLat}} \otimes I_{\catname{SLat}}))\\
            &\cong \coprod_{A} (\coprod_{B} I_{\catname{SLat}})\\
            &\cong \coprod_{A \times B} I_{\catname{SLat}}\\
            &\cong F(A \times B)
      \end{align*}
    In the above we used the fact that functors $- \otimes X$ and $X \otimes -$ preserve colimits as they are both left-adjoint by symmetry and monoidal closedness of $\catname{SLat}$.
    \end{proof}
